\documentclass[12pt]{article}
\usepackage[left=1in, right=1in, top=0.25in, bottom=1in]{geometry}
\begin{document}
\author{Armon Shariati}
\title{}
\date{}
\maketitle

Forty-five years ago, the Iranian monarchy was dissolved to pave the way for
the Islamic Republic. In the process, members of the generations old Persian
aristocracy were detained, had all their possessions stripped from them, and
often times were executed. However, many of those who rose to power during this
time never forgot how they were treated by the aristocratic families that
governed their lands. Furthermore, by the virtue of the great lengths my
mother's family - one of the oldest and most influential - had gone to protect
and provide for the people they were responsible for, many gave their lives to
ensure they were spared. This is the legacy my mother always sought to uphold.
She had told me that she became a transplant surgeon for three reasons. First,
it had always been her passion since she saw an American surgeon save her
mother's life.  Second, protecting human life had always been a sacred
cornerstone of her family's values. Thirdly, she wanted to ensure that her
children's ambitions would never be driven by money. Ultimately, she was
successful. My mother used her resources to educate her children about the
world.  By my eighteenth birthday, I had studied abroad in four different
countries and visited twelve.  I had volunteered as both an EMT at a Belizean
medical clinic and a skipper's assistant aboard a catamaran touring the
Caribbean.  None of the luxuries or experiences life had to offer were out of
reach. Yet, despite all of these indulgences, I felt empty. I had no passion.
I was terrified by the thought of spending my life being the last link in a
long chain of heroes, and to do nothing to uphold that tradition.

I arrived at Lehigh University insatiably curious. I had applied as an English
major, with a strong interest in Philosophy.  Up until this point, I had
thought literature had been my calling. However, I knew my zeal for English
paled in comparison to how my mother felt about medicine. By some twist of
fortune, I was forced to take Introduction to Computer Science my first
semester because all of the electives I was interested in, such as Greek
Tragedy, were full. I did not expect to see that the same flow of logic I used
to analyze literature appeared in writing software. Quickly, my interest
devolved into an obsession.  Within the first few weeks of the semester I
tirelessly asked numerous professors for opportunities to work with them.  With
absolutely zero background in technology, my pleas fell on deaf ears.
Professor Michael Spear was the only one to take me seriously. Together, we
developed a robotics platform that leveraged the computational capacity and
compact form factor of Android smart phones. We created a fun set of demos and
took them to a local elementary school to generate interest in STEM fields.
Looking back, the task was charmingly elementary. However, while the
satisfaction of instilling the smallest amount of excitement into the
elementary school students was a sufficient reward itself, I learned much in my
time working with Professor Spear.  I learned how to manage frustration, to
become self-reliant, and the importance of education outside the classroom, all
of which became the seeds to my later love for research.

Professor Spear noticed my growing interest in robotics and put me in touch
with Professor John Spletzer, who later extended me the opportunity to work in
his laboratory as an REU student in the summer of 2013. My first experience
with research was far from what I expected, and I faced as many technical
challenges as I did personal challenges.  My mentor's name was Dylan
Schwesinger, a PhD student with absolutely zero tolerance for mediocrity.
Being so young and naive, I took many of his stern teachings personally and
quickly became frustrated with the seemingly impossible tasks he would delegate
to me. Ultimately, he made me question if this was indeed the path I wanted to
take.  I knew that this had to be my passion, because in those lowest moments
of self-doubt and confusion, I constantly found the answer to be yes. At the
time, I was utterly blind to what Dylan was trying to do for me. I had been
full of pride in light of my previous accomplishments, and by forcing me to
confront my own ignorance and ego, I became humbled and patient, ready to begin
learning for its own sake. Since I started working in VADER lab nearly a year
and a half ago, I have spent every day under Dylan's tutelage.  He taught me
how to engineer software by making me wallow and suffer with any code I wrote.
He taught me how to start generalizing theoretical mathematical concepts for
use as engineering tools. He taught me to take pride in any aspect of
development I am a part of, and to never deliver any less than my best work.
His lessons paid off as I was able to contribute enough to our lab's research
in order to become a co-author on both a conference paper and a recent
journal submission. I even had the opportunity to present our work at an
internationally recognized conference. In time, Dylan became one of my best
friends. Only then did I understand that he wouldn't have pushed me as hard as
he did if he did not believe I had the potential and mindset to go the
distance.

At the end of my junior year, I was selected to participate in the NSF
sponsored, GRASP REU program at the University of Pennsylvania during the
summer of 2014. I had originally been accepted to the program to work with
Professor CJ Taylor on vision based mobile systems, which had also been the focus
of my previous work at VADER. To my surprise, upon my arrival Professor Taylor
asked me to work on a project where I had no prior experience with either of
the fields involved, graphics and haptics. The vision for the project was to
develop a general platform for creating virtual reality applications that
integrate cutting edge haptic devices with state of the art gaming displays.
In addition to having no prior experience or interest with either discipline, I
had never been responsible for the entire design of a system of this size from
scratch.  However, using the lessons I had learned from past research
experience, I quickly set up a development environment, acquainted myself with
the basics of graphics and haptics, and devised a plan to have a working system
by the end of the summer. I also discovered how fascinating both subjects were,
and how vision problems and graphics problems were so interrelated. At the end
of the program, I had finished a demo and even won the award for best REU
research paper. In the fall, I had an abstract accepted by the Northeast
Robotics Colloquium, where I presented my work in a poster session.  However,
more important than the successful project itself was learning to stay open
minded when dealing with technologies I am unfamiliar with, and learning to
quickly absorb whatever knowledge is necessary to complete a task.

At the onset of my senior year, I have finally acquired the skills to spearhead
a graduate-level research project, the Lehigh Mapping Tricycle (LMT). The LMT
project is motivated by the lack of means to construct large-scale feature maps
in outdoor urban environments required for our Smart Wheelchair System.  Data
from the LMT's proprioceptive sensors including a GPS module, an IMU, and
encoder, are fused together to generate an estimate of its position in 3D
space. With 3D odometry in place, vertical LIDAR scans taken from either side
of the vehicle are aggregated in order to create a 3D point cloud, from which
pole-like features are extracted for mapping. Using variations of SLAM, the
locations of poles are optimized over the path the robot has taken in order to
generate a 2D map.  After inheriting the majority of the hardware, I wrote the
software for robust pose estimation, pole segmentation, and map generation. The
work I have completed as of December 2014 has even been incorporated as a
section in our latest aforementioned journal submission. I am beginning to
comprehend what it means to be a researcher. With no more than a few
suggestions in passing from my adviser or graduate mentor as I incur some of
the largest challenges, I am responsible for thinking of my own creative
solutions. I independently devise experiments, and assess their merit.  Perhaps
the most daunting challenge of all is finding the time  and energy to address
the other aspects of my life as I constantly find myself saying, ``let me just
finish this one last thing and then I'll go home''. Although, when I come home
at night and lay on my bed exhausted, I can't help but to feel the most
overwhelming sensation of fulfillment.

Disaster relief is a fascinating problem domain where many current solutions
are telerobotic systems. However, advancements in sensing, computing, and
manufacturing technology, coupled with the high cost of training specialized
personnel, have caused a recent surge of research interest in developing
autonomous agents. The DARPA robotics challenge is a testament to the shift in
research trends. In graduate school, I would like to investigate the use of
more advanced object recognition techniques, such as scene parsing, in order to
provide planning cues to robots navigating in disaster zones and other dynamic
environments.  These settings contain high degrees of uncertainty and would be
inappropriate to model with static obstacle assumptions. Effective object
recognition in such environments could be invaluable, setting the stage for new
approaches towards planning and decision making. I can see these technologies
having a drastic effect on how we handle natural disasters and crisis, which
would ultimately save more lives. Becoming a professor in the field of robotics
has become my dream. Being a professor is unique in the sense that I could
simultaneously commit myself to developing useful technology that helps and
protects people, and - just as Professor Spear, Professor Spletzer, and Dylan
had done for me - I could make a difference in the lives of those I would
inevitably teach. I finally discovered a path that is consistent with my own
passions and yet honors the legacy I am a part of, just like my mother.

I am incredibly grateful for the education Lehigh has given me. Having worked
in such a small laboratory, I was forced early on to learn as much as I could
about various disciplines from manufacturing, to controls design, to planning
and perception. In addition, working within more modest research budgets made
me appreciate the tools I have at my disposal. I knew when I was not ready both
in skill and in spirit when I was first rejected by MIT as an undergraduate
transfer student my freshman year. I am applying to MIT now for my PhD with a
purpose. I want to earn my degree at MIT because that would mean having the
opportunity to work alongside some of the most celebrated researchers such as
Nicholas Roy, Russ Tedrake, Daniella Rus, and Leslie Kaelbling. It is really a
matter of numbers. Simply based on the number of talented people working at
MIT, one is constantly exposed by a plethora of ideas and information from a
broad range of fields which always seem to inspire one's own work. The
education MIT has to offer me is only available at less than a handful of
places on the planet. Not only can I understand what a privilege it would be to
a part of the community, but I would use that privilege to the best of my
ability in order to pursue my dream and honor the institution that would make
it possible.
\end{document}
